The transition redshift as a probe of reionization

### 2019-08-11 paper/ms.tex
Add some commands
Update short title
Slightly modify abstract

@@

\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[The transition redshift]{The transition redshift as a probe of reionization}

@@

% Abstract of the paper
\begin{abstract}
The early stages of the Epoch of Reionization (EoR), probed by the 21~cm line,
are sensitive to the detailed formation of the first galaxies. An important
transition occurs on large scales at $\avg{x_i}\sim0.15$, when the 21~cm field
transitions from being positively correlated with the galaxy field to being
negatively correlated. The redshift at which this transition occurs (the
``transition redshift'') is, in principle, sensitive to both the structure of
the 21~cm field but also the galaxy field. However, by considering a fixed
model for the EoR and varying the parameters of a simple model for the galaxy
field in a mock [O~\textsc{iii}]-emitter sample cross-correlation, we show
that the transition redshift is in fact insensitive to the structure of the
selected galaxy sample. We show that prospects for measuring the transition
redshift are feasible in the near-term with a combination of LOFAR and JWST.
Being derived from a cross-correlation, the transition redshift is less
impacted by foreground contamination currently inhibiting 21~cm auto-spectrum
measurements. Therefore, the transition redshift is a promising probe of the
early stages of the EoR.
\end{abstract}

>>>>

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

@@

\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\HII}{\ensuremath{\text{H~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\kpc}{\ensuremath{\text{kpc}}}
\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
\newcommand{\Myr}{\ensuremath{\text{Myr}}}
\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
\newcommand{\kms}{\ensuremath{\text{km}\,\text{s}^{-1}}}

\newcommand{\fid}{\texttt{fid}}
\newcommand{\hot}{\texttt{hot}}
\newcommand{\cold}{\texttt{cold}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[The transition redshift as an EoR probe]{The transition redshift as a probe of reionization}

@@

% Abstract of the paper
\begin{abstract}
The early stages of the Epoch of Reionization (EoR), probed by the 21~cm line,
are sensitive to the detailed formation of the first galaxies. An important
transition occurs on large scales at $\avg{x_i}\sim0.15$, when the 21~cm field
transitions from being positively correlated with the galaxy field to being
negatively correlated. The redshift at which this transition occurs (the
``transition redshift'') is, in principle, sensitive to both the structure of
the 21~cm field but also the galaxy field. However, by considering a fixed
model for the EoR and varying the parameters of a simple model for the galaxy
field in a mock [O~\textsc{iii}]-emitter sample cross-correlation, we show
that the transition redshift is in fact insensitive to the structure of the
selected galaxy sample. We show that prospects for measuring the transition
redshift are feasible in the near-term with a combination of LOFAR and JWST.
Being derived from a cross-correlation, the transition redshift is less
impacted by foreground contamination currently inhibiting 21~cm auto-spectrum
measurements. Therefore, the transition redshift is an interesting probe of
the early stages of the EoR, and its detectability and interpretability
deserve further study.
\end{abstract}
